---
title: "Homework 3 dada2 setup - Spring 2019 - ANSWER KEY "
author: "Melinda Higgins"
date: "March 25, 2019"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Document package installation

Use `library()` function to load each package to show that the packages are installed.

You have to use the BioConductor approach and tools to install the `dada2` (which includes `Shortread`), `phyloseq` and `DECIPHER`. I installed my packages using a separate R script (see "packages_install.R" stored in this Github repository). But here is the script code to install these packages.

```
# install BiocManager

if (!requireNamespace("BiocManager"))
  install.packages("BiocManager")
BiocManager::install()

# install dada2 - includes ShortRead pacakge

if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install("dada2", version = "3.8")

# install phyloseq

if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install("phyloseq", version = "3.8")

# install DECIPHER

if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install("DECIPHER", version = "3.8")
```

`ggplot2` can be installed from CRAN using the RStudio /Tools/Install Packages menu.

```{r}
library(dada2)
library(ShortRead)
library(phyloseq)
library(DECIPHER)
library(ggplot2)
```

## Shows you've downloaded the `fastq` files

The `dada2` tutorial explains this part at [http://benjjneb.github.io/dada2/tutorial.html](http://benjjneb.github.io/dada2/tutorial.html).

```{r}
# CHANGE ME to the directory containing the fastq files after unzipping.
# path <- "~/MiSeq_SOP" # MAC path specification
path <- "./MiSeq_SOP" # PC path specification
list.files(path)
```

## Get the Silva 132 training set and the Silva 132 species assignment zip files

see [https://zenodo.org/record/1172783#.XJkdyKBKiUl](https://zenodo.org/record/1172783#.XJkdyKBKiUl)

Put these 2 `*.gz` files into the same directory as specified above.

## Get SILVA SSU r132 RData object

See [http://www2.decipher.codes/Downloads.html](http://www2.decipher.codes/Downloads.html) - download the training file for Silva SSU r132. This is a `RData` file. Put in same directory as above.

List files again 

```{r}
path <- "./MiSeq_SOP"
list.files(path)
```

